### 2018-05-24 Paper/app.tex
..

In this study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
lean. Consider the global reaction:

\be
2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2O
\label{eq:global}
\ee 
%
The equivalence ratio ($\phi$) is defined as follows:
%
\be
\phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
\ee
%
The numerator in the RHS represents the fuel-oxygen mass ratio at a given condition
and the denominator represents the stoichiometric ratio of the same quantity. Hence,
$\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
by changing the amount of O$_2$ in the mixture. Essentially, $\phi>1$ corresponds to
a rich mixture, and $\phi<1$ corresponds to a lean mixture. The above
reaction~\eqref{eq:global} could thus be generalized as follows:

\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\min(1,\alpha)\text{H}_2\text{O} + 
\max(\alpha-1,0)\text{O}_2 + \max(0,2-2\alpha)\text{H}_2
\label{eq:gen}
\ee

>>>>

In this study, we focus on two scenarios: fuel(H$_2$) rich, and fuel(H$_2$)
lean. Consider the global reaction:
%
\be
2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
\label{eq:global}
\ee 
%
The equivalence ratio ($\phi$) is defined as follows:
%
\be
\phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
\label{eq:phi}
\ee
%
The numerator in the RHS represents the fuel-oxygen mass ratio at a given condition
and the denominator represents the stoichiometric ratio of the same quantity. Hence,
$\phi$ = 1 at stoichiometric conditions. The equivalence ratio can be altered
by changing the amount of O$_2$ in the mixture. In the case of a lean
mixture,~\eqref{eq:global} can be written as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\text{H}_2\text{O} + (\alpha-1)\text{O}_2 
\hspace{3mm} (\alpha>1)
\label{eq:lean}
\ee 
%
Similarly, for the case when the mixture if fuel rich,~\eqref{eq:global} is modified
as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\alpha\text{H}_2\text{O} + 2(1-\alpha)\text{H}_2
\hspace{3mm} (\alpha<1)
\label{eq:rich}
\ee 
%
Eqs.~\eqref{eq:lean} and~\eqref{eq:rich} can be generalized as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\min(1,\alpha)\text{H}_2\text{O} + 
\max(\alpha-1,0)\text{O}_2 + \max(0,2-2\alpha)\text{H}_2
\label{eq:gen}
\ee 
%
From the above set of chemical equations, the relationship between $\phi$
and $\alpha$ can be easily obtained as $\left(\phi~=~\frac{1}{\alpha}\right)$.
Since $\phi>1$ corresponds to a rich mixture, and $\phi<1$ corresponds to a
lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
respectively.
